\vspace{-1cm} Progress Report: UNet-CRF Integration for Sequence Labeling on EEG Data

### 2024-11-11 progress/progress.tex
minor
rename the project

\usepackage[left=.5in, right=.5in, top=.3in, bottom=.3in]{geometry}
\usepackage{amsfonts,amsmath,amssymb}
\usepackage{authblk}
%% put affiliations into one line
\makeatletter
\renewcommand\AB@affilsepx{\quad\protect\Affilfont}
\usepackage{bbm}
\usepackage[inline]{enumitem}
\usepackage{graphicx}
\graphicspath{{./}{../image/}}
\usepackage[colorlinks=true,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}
\usepackage{setspace}
\setstretch{1.2}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{8pt}{8pt}

@@

\title{\vspace{-1cm} \Large
Progress Report: Transformer-CRF Integration for Sequence Labeling on EEG Data}

@@

After building the theoretical model formualtion of our project, we also
finished preliminary analyses of the data. Our preprocessed spectrograms
dataset that are ready for training model. The dataset will be available on
\href{https://github.com/Carol-seven/Transformer-CRF_EEG}{GitHub} and
made public after the project is completed.

@@

\footnotesize
\bibliography{../manuscript/refs}
\bibliographystyle{chicago}

>>>>

\usepackage[left=.5in, right=.5in, top=.3in, bottom=.3in]{geometry}
\usepackage{amsfonts,amsmath,amssymb}
\usepackage{authblk}
%% put affiliations into one line
\makeatletter
\renewcommand\AB@affilsepx{\quad\protect\Affilfont}
\usepackage{bbm}
\usepackage[inline]{enumitem}
\usepackage{graphicx}
\graphicspath{{./}{../image/}}
\usepackage[colorlinks=true,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}
\usepackage{setspace}
\setstretch{1.2}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{5pt}{5pt}

@@

\title{\vspace{-1cm}
Progress Report: UNet-CRF Integration for Sequence Labeling on EEG Data}

@@

After building the theoretical model formualtion of our project, we also
finished preliminary analyses of the data. Our preprocessed spectrograms
dataset that are ready for training model. The dataset will be available on
\href{https://github.com/Carol-seven/UNet-CRF_EEG}{GitHub} and
made public after the project is completed.

@@

\bibliography{../manuscript/refs}
\bibliographystyle{chicago}
